\section{Additional features}
In addition to the technologies that are visible to users of the site, or which have been mentioned elsewhere in this report, the following are also in use:
\begin{description}
    \item[Search engine optimization (SEO).] A priority of the site has been that it be accessible and findable by as many people as possible. As a result, creating a site that is optimized for search engine access and crawling has been a priority. The site has search engine-friendly markup throughout, has an indexed sitemap containing a link to all of the documents in the corpus, and pings all of the major search engines whenever the sitemap has major changes.\footnote{For details about sitemap specification and purpose, see http://sitemaps.org.} Additionally, because each document in the website can be accessed via a link to its case name, number or SHA1 hash, a canonical link is provided in the HTML header to inform search engines that the two URIs are the same.\footnote{http://googlewebmastercentral.blogspot.com/2009/02/specify-your-canonical.html.}
    \item[OpenSearch plugin.] A browser search tool is available on the site to allow users to query the database directly from their browser.
    \item[Traffic and usage monitoring.] In order to monitor the traffic and usage of the site, I have installed and configured the Piwik open source web analytics package. It provides tracking services similar to third party tracking services, but allows the tracking to be self-served, and thus more private. In addition, administrators using the site are not tracked, making the generated statistics as accurate as possible.
    \item[Privacy policy and implementation.] Although the site collects very little private information, it is configured to delete all logs after 12 weeks, and has a clear privacy policy indicating what information is collected and how long it is kept.
    \item[Atom specification.] For the RSS feeds that are provided on the site, the Atom specification has been chosen for its strict XML conformance. Atom feeds are provided for each court, and can also be dynamically created via the search interface.
    \item[Caching.] Caching is completed on four basic levels. Memcached caches the pages of the site in their final form, MySQL caches database queries, and Apache caches compiled versions of the django settings and programs. Finally, the page describing the coverage of the site is generated once nightly and is cached in the database.
    \item[User profiles.] User profiles have been set up with complete features, including account deletion, password reset, forgotten password assistance, and profile configuration.
    \item[Bug tracking.] Bugs are being tracked on the project page, with 56 beta-targeted bugs closed, and an additional 35 bugs targeted at version 1.0.
\end{description}
